---
title: "IMF World Economic Outlook Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: lumen
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
load("Data/WEOpanelApr2021.Rdata")
load("Data/WEOcodebook.Rdata")
full_weo$Version <- as.factor(full_weo$Version)
full_weo <- full_weo %>% 
  mutate(Version = factor(Version, levels=c("oct2019", "oct2020", "apr2021")))
countries <- unique(full_weo$Country)
years <- unique(full_weo$year)
vintages <- unique(full_weo$Version)
variables <- unique(code_book$WEO.Subject.Code)
```

Single Country
==================

Column {.sidebar data-width=200}
-----------------------------------------------------------------------

This visualization compares the October 2019, October 2020 and April 2021 vintages of the World Economic Outlook data and forecasts, published by the IMF. 
\n Author: Henrique Barbosa


```{r}
selectInput("ctry", label = "Country: ",
            choices = countries, selected = "Brazil")

selectInput("year1", label = "From: ",
            choices = years, selected = 2019)

selectInput("year2", label = "To: ",
            choices = years, selected = 2023)

```


Column {data-width=400}
-----------------------------------------------------------------------

### Unemployment Rate (%)



```{r}

renderPlot({
  
  full_weo %>% 
    filter(Country == as.character(input$ctry) & year>=(input$year1) & year <= (input$year2)) %>%
    ggplot(aes(y=LUR, x=year, fill=Version)) + 
    geom_bar(position="dodge", stat="identity") +
    geom_text(aes(label=LUR), vjust=-0.3, color="black",
                                              position = position_dodge(0.9), size=3) +
    theme(axis.title.x=element_blank(), axis.title.y=element_blank()) +
    guides(fill=guide_legend(title="WEO Vintage"))
    
})
```

### General Government Gross Debt (% of GDP)


```{r}
renderPlot({
  full_weo %>% filter(Country == as.character(input$ctry) & year>2018 & year < 2024) %>% 
    ggplot(aes(y=GGXWDG_NGDP, x=year, fill=Version)) + 
    geom_bar(position="dodge", stat="identity") +
    theme(axis.title.x=element_blank(), axis.title.y=element_blank()) +
        geom_text(aes(label=GGXWDG_NGDP), vjust=-0.3, color="black",
                                              position = position_dodge(0.9), size=3) +
    coord_cartesian(ylim=c(20,NA)) +
    guides(fill=guide_legend(title="WEO Vintage"))

})
```

Column {data-width=400}
-----------------------------------------------------------------------

### Real GDP growth (%)

```{r}
renderPlot({
full_weo %>% filter(Country == as.character(input$ctry) & year>2018 & year < 2024) %>% 
    ggplot(aes(y=NGDP_RPCH, x=year, fill=Version)) + 
    geom_bar(position="dodge", stat="identity") +
    geom_text(aes(label=NGDP_RPCH), vjust=-0.3, color="black",
                                              position = position_dodge(0.9), size=3) +
    theme(axis.title.x=element_blank(), axis.title.y=element_blank()) +
    guides(fill=guide_legend(title="WEO Vintage"))
})
```

### Nominal GDP path

```{r}
renderPlot({
full_weo %>%
  filter(Country == as.character(input$ctry) & year>2010 & year < 2024) %>% 
    ggplot(aes(x=year, y=NGDP_R, group=Version, color = Version)) + 
    geom_line() +
    geom_path(size=1) +
    theme(axis.title.x=element_blank(), axis.title.y=element_blank()) +
    guides(fill=guide_legend(title="WEO Vintage")) 
})
```

Cross-Country 
==================

Column {.sidebar data-width=200}
-----------------------------------------------------------------------

This visualization compares the October 2019, October 2020 and April 2021 vintages of the World Economic Outlook data and forecasts, published by the IMF. 
\n Author: Henrique Barbosa


```{r}
selectInput("weovintage", label = "WEO Vintage: ",
            choices = vintages, selected = "apr2021")

selectInput("ctry1", label = "Country 1: ",
            choices = countries, selected = "Brazil")

selectInput("ctry2", label = "Country 2: ",
            choices = countries, selected = "India")

selectInput("ctry3", label = "Country 3: ",
            choices = countries, selected = "Mexico")

selectInput("year3", label = "From: ",
            choices = years, selected = 2015)

selectInput("year4", label = "To: ",
            choices = years, selected = 2024)

```


Column {data-width=800}{data-height=100%}
-----------------------------------------------------------------------

### Real GDP growth (%)
```{r}
renderPlot({
  full_weo %>% filter(Country %in% as.character(c(input$ctry1, input$ctry2, input$ctry3)) 
                      & year>(input$year3) & year < (input$year4)
                      & Version==as.character(input$weovintage)) %>% 
    ggplot(aes(y=NGDP_RPCH, x=year, fill=Country)) + 
    geom_bar(position="dodge", stat="identity") +
    theme(axis.title.x=element_blank(), axis.title.y=element_blank()) +
        geom_text(aes(label=NGDP_RPCH), vjust=-0.3, color="black",
                                              position = position_dodge(0.9), size=3) +
    guides(fill=guide_legend(title="Country"))

})
```

### General Government Gross Debt (% of GDP)
```{r}
renderPlot({
  full_weo %>% filter(Country %in% as.character(c(input$ctry1, input$ctry2, input$ctry3)) 
                      & year > (input$year3) & year < (input$year4)
                      & Version==as.character(input$weovintage)) %>%  
    ggplot(aes(y=GGXWDG_NGDP, x=year, fill=Country)) + 
    geom_bar(position="dodge", stat="identity") +
    theme(axis.title.x=element_blank(), axis.title.y=element_blank()) +
        geom_text(aes(label=GGXWDG_NGDP), vjust=-0.3, color="black",
                                              position = position_dodge(0.9), size=3) +
    coord_cartesian(ylim=c(20,NA)) +
    guides(fill=guide_legend(title="Country"))

})
```

All Variables {vertical_layout=scroll}
==================

Column {.sidebar data-width=200}
-----------------------------------------------------------------------

This visualization compares the October 2019, October 2020 and April 2021 vintages of the World Economic Outlook data and forecasts, published by the IMF. 
\n Author: Henrique Barbosa


```{r}

selectInput("weovintage2", label = "WEO Vintage: ",
            choices = vintages, selected = "apr2021")

selectInput("ctry4", label = "Country: ",
            choices = countries, selected = "Brazil")

selectInput("year5", label = "From: ",
            choices = years, selected = 2015)

selectInput("year6", label = "To: ",
            choices = years, selected = 2024)

selectInput("var1", label = "Chart 1 Variable: ",
            choices = variables, selected = "BCA")

selectInput("var2", label = "Chart 2 Variable: ",
            choices = variables, selected = "LUR")

```


Column {data-width=800}
-----------------------------------------------------------------------

### Chart 1
```{r}
renderPlot({
  full_weo %>% filter(Country == input$ctry4
                      & year>(input$year5) & year < (input$year6)
                      & Version==as.character(input$weovintage2)) %>% 
    ggplot(aes(y=input$var1, x=year, fill=Country)) + 
    geom_bar(position="dodge", stat="identity") +
    theme(axis.title.x=element_blank(), axis.title.y=element_blank()) +
        geom_text(aes(label=input$var1), vjust=-0.3, color="black",
                                              position = position_dodge(0.9), size=3) +
    guides(fill=guide_legend(title="Country"))

})
```

### Chart 2
```{r}
renderPlot({
  full_weo %>% filter(Country == input$ctry4
                      & year > (input$year5) & year < (input$year6)
                      & Version==as.character(input$weovintage2)) %>%  
    ggplot(aes(y=input$var2, x=year, fill=Country)) + 
    geom_bar(position="dodge", stat="identity") +
    theme(axis.title.x=element_blank(), axis.title.y=element_blank()) +
        geom_text(aes(label=input$var2), vjust=-0.3, color="black",
                                              position = position_dodge(0.9), size=3) +
    coord_cartesian(ylim=c(20,NA)) +
    guides(fill=guide_legend(title="Country"))

})
```

### Variable names and definitions
```{r}
renderTable({
  code_book
})
```

